\documentclass[11pt,a4paper]{article}
%\pdfoutput=1 % if your are submitting a pdflatex (i.e. if you have
             % images in pdf, png or jpg format)
             
\synctex=1
\usepackage{float}
\usepackage{jheppub} % for details on the use of the package, please
                     % see the JHEP-author-manual

\usepackage{braket,slashed,bm}
\usepackage{array,multirow}
\usepackage[normalem]{ulem}
\usepackage{cancel}
\usepackage[table]{xcolor}
\usepackage[vcentermath]{youngtab}

\usepackage[T1]{fontenc} % if needed

\usepackage{mathrsfs}

\usepackage{booktabs}
\usepackage{adjustbox}
\usepackage{mathtools}

\usepackage{soul}

\usepackage{arydshln}
\usepackage[utf8]{inputenc}

\def\nn{\nonumber\\ }
\def\hyp{\mathsf{y}}

\renewcommand{\O}{\mathcal{O}}
\newcommand{\hc}{\mathrm{h.c.}}

\begin{document}
%%----------------------------------------------------------------------------------------------------------------------------------------------------------------

\title{Dimension-8 Operators in the Standard Model Effective Field Theory}

\author{Christopher W.~Murphy}

\abstract{
We present a complete basis of dimension-8 operators in the Standard Model Effective Field Theory.
Attention is paid to operators that vanish in the absence of flavor structure.
There are dimension-8 SMEFT 44,807 operators.
We also briefly discuss a few aspects of phenomenology involving dimension-8 operators, including light-by-light scattering and electroweak precision data.
}
\maketitle

%%----------------------------------------------------------------------------------------------------------------------------------------------------------------

\section{Introduction}
\label{sec:intro}

\input{sections/intro_v5}

%%----------------------------------------------------------------------------------------------------------------------------------------------------------------

\section{Notation and Conventions}
\label{sec:note}

\input{sections/conventions_v2}

%%----------------------------------------------------------------------------------------------------------------------------------------------------------------

\section{Operator Classification}
\label{sec:cls_ops}

\input{sections/operator_classification_v5}

%%----------------------------------------------------------------------------------------------------------------------------------------------------------------

\section{The Complete Set of Dimension-8 Operators}
\label{sec:results}

\input{sections/results_v5}

%--------------------------------------------------------------------------------------------------------------
\subsection{Results for Bosonic Operators}

See Tables~\ref{tab:smeft8class_1_2_3_4} and \ref{tab:smeft8class_5_6_7_8}.

\input{sections/dim8_classes_1_2_3_4}

\input{sections/dim8_classes_5_6_7_8_v2}

%--------------------------------------------------------------------------------------------------------------
\subsection{Results for Two-Fermion Operators}

See Tables~\ref{tab:smeft8class_9}, \ref{tab:smeft8class_10_11_12_13}, \ref{tab:smeft8class_14qud}, \ref{tab:smeft8class_14le_15RR}, \ref{tab:smeft8class_15LL}, and \ref{tab:smeft8class_16_17}.

\input{sections/dim8_classes_9}

\input{sections/dim8_classes_10_11_12_13_v2}

\input{sections/dim8_classes_14_v2}

\input{sections/dim8_classes_15}

\input{sections/dim8_classes_16_17}

%--------------------------------------------------------------------------------------------------------------
\subsection{Results for Four-Fermion Operators}

See Tables~\ref{tab:smeft8class_18_21}, \ref{tab:smeft8class_18},  \ref{tab:smeft8class_19_LL_RR}, \ref{tab:smeft8class_19_LLRR}, \ref{tab:smeft8class_19_LRRL_LRLR}, \ref{tab:smeft8class_19_slashedB}, \ref{tab:smeft8class_20_le_qu}, \ref{tab:smeft8class_20_qd_slashedB}, and \ref{tab:smeft8class_21}.


\input{sections/dim8_classes_18_v6}

\input{sections/dim8_classes_19_v6}

\input{sections/dim8_classes_20}

\input{sections/dim8_classes_21_v3}

%%----------------------------------------------------------------------------------------------------------------------------------------------------------------

\section{Phenomenology}
\label{sec:pheno}

\input{sections/pheno_v4}

%%----------------------------------------------------------------------------------------------------------------------------------------------------------------

\section{Comments on Renormalization Group Evolution}
\label{sec:rge}

\input{sections/rge}

%%----------------------------------------------------------------------------------------------------------------------------------------------------------------

\section{Conclusions}
\label{sec:con}

\input{sections/conclusion_v5}


%%----------------------------------------------------------------------------------------------------------------------------------------------------------------

\section*{Acknowledgements}
\addcontentsline{toc}{section}{Acknowledgements}

We thank Renato Fonseca, Adam Martin, Grant Remmen, Nicholas Rodd, Ver\'onica Sanz, Michael Trott for useful discussions.
The author is grateful for the privilege of being able to stay home and work on a project like this.
Ref.~\cite{Li:2020gnx} appeared on the arXiv simultaneously with this work.
It also presents a complete basis of dimension-8 SMEFT operators.
We are especially grateful to Jing Shu and Jiang-Hao Yu for discussions of Ref.~\cite{Li:2020gnx}.

Additionally, there were a few issues in original version of the paper.
(v2 on the arXiv is the JHEP version.)
We would also like to thank:
\begin{itemize}
\item [v3] Marco Ardu for finding a mistake in $Q_{leqdH^2}^{(4)}$
\item [v4] Mikael Chala for finding a couple of mistakes in the matching in Section~\ref{sec:quartets}
\item [v5] Serge Hamoudou, Jacky Kumar, and David London for demonstrating the flavor indices were incorrect on the right-hand side of the bottommost equation in~\eqref{eq:l5} and that the operator $Q_{q^4H^2}^{(5)}$ was originally missing from the basis
\item [v6] Serge Hamoudou for helping identify that the combination $\epsilon \tau^I$ ($\tau^I \epsilon$) should go with a pair of $SU(2)_w$ (anti-)fermions.
\end{itemize}


%%----------------------------------------------------------------------------------------------------------------------------------------------------------------

\begin{appendix}


\input{sections/appendix_v6}

\end{appendix}

\clearpage

%%----------------------------------------------------------------------------------------------------------------------------------------------------------------

\bibliographystyle{JHEP}
\bibliography{dim8}

%%----------------------------------------------------------------------------------------------------------------------------------------------------------------

\end{document}
